---
title: 'DS 202: Final Project'
author: "Muhammad Khairi Norizan"
date: "11/28/2021"
output: html_document
---

```{r setup, include=FALSE}
# import library 
library(tidyverse)
library(lubridate)
library(ggplot2)
library(dplyr)
library(readxl)

# importing dataset
netflix <- read_excel('./Dataset/Netflix Dataset Latest 2021.xlsx', sheet='FlixGem.com dataset')
amazon <- read_csv("./Dataset/amazon_prime_titles.csv") 
netflix_amazon <- read_csv("./Dataset/Popular Movies TV shows from Prime Videos Netflix version_3.csv") 
```

## Data Engineering
```{r, warning=FALSE, message=FALSE}
# extract only amazon data
amazon2 <- netflix_amazon %>% filter(`Amazon Prime Video` == 1)

# extract only netflix data
netflix2 <- netflix_amazon %>% filter(Netflix == 1)

# join dataset
netflix <- netflix %>% inner_join(netflix2, by = c("Title" = "Title"))
amazon <- amazon2 %>% inner_join(amazon, by = c("Title" = "title"))

# cleaning dataset
netflix <- netflix %>% 
            select(Title, Genre.x, Tags, Languages, `Series or Movie`, `Country Availability`, 
                   Runtime, Director, Writer, `View Rating`, `IMDb Score`, `Rotten Tomatoes Score`, 
                   `Awards Received`, `Awards Nominated For`, `Release Date`, `Netflix Release Date`, 
                   `IMDb Votes`, Year) %>% 
            rename(Genre = Genre.x, `Series/Movie` = `Series or Movie`) %>% 
            distinct(Title, .keep_all = TRUE)

amazon <- amazon %>% 
          select(Title, Year, rating, IMDb, `Rotten Tomatoes`, 
                 Genre, type, director, country, date_added, release_year, duration)
amazon$IMDb <- as.numeric(amazon$IMDb)
amazon$`Rotten Tomatoes` <- as.numeric(amazon$`Rotten Tomatoes`)
```

## Exploration

1. Find the number of Movies and TV shows, and find the average IMDb and Rotten Tomatoes score.
```{r, message=FALSE}
amazon_movies_series_count <- amazon %>% 
                              group_by(type) %>% 
                              summarize(count = n())

netflix_movies_series_count <- netflix %>% 
                                group_by(`Series/Movie`) %>% 
                                summarize(count = n())

netflix_movies_series_count$`Series/Movie`[netflix_movies_series_count$`Series/Movie` == 'Series'] <- 'TV Show'

movies_series_count <- amazon_movies_series_count %>% 
                        full_join(netflix_movies_series_count) %>% 
                        rename(Amazon = type, Netflix = `Series/Movie`)

movies_series_count <- movies_series_count[, c("count", "Amazon", "Netflix")]

movies_series_count <- movies_series_count %>% 
                        pivot_longer(Amazon:Netflix, names_to = "Stream", values_to = "Type") %>% 
                        filter(!is.na(Type))

ggplot(movies_series_count, aes(x=Type, y=count, fill = Stream)) +
  geom_bar(stat = "identity", position=position_dodge()) + 
    scale_fill_manual(values=c('#999999','#E69F00'))
```

```{r, message=FALSE, warning=FALSE}
amazon_movies_series_avg_rating <- amazon %>% 
                                    group_by(type) %>% 
                                    summarize(AvgImdbScore = mean(na.omit(IMDb)), 
                                              AvgRottenTomatoesScore = mean(na.omit(`Rotten Tomatoes`)))

netflix_movies_series_avg_rating <- netflix %>% 
                                    group_by(`Series/Movie`) %>% 
                                    summarize(AvgImdbScore = mean(na.omit(`IMDb Score`)), 
                                              AvgRottenTomatoesScore = mean(na.omit(`Rotten Tomatoes Score`)))

netflix_movies_series_avg_rating$`Series/Movie`[netflix_movies_series_avg_rating$`Series/Movie` == 'Series'] <- 'TV Show'

movies_series_avg_rating <- amazon_movies_series_avg_rating %>% 
                            full_join(netflix_movies_series_avg_rating) %>% 
                            rename(Amazon = type, Netflix = `Series/Movie`)

movies_series_avg_rating <- movies_series_avg_rating[, c("AvgImdbScore", "AvgRottenTomatoesScore", 
                                                         "Amazon", "Netflix")]

movies_series_avg_rating <- movies_series_avg_rating %>% 
                            pivot_longer(Amazon:Netflix, names_to = "Stream", values_to = "Type") %>% 
                            filter(!is.na(Type))

ggplot(movies_series_avg_rating, aes(x = Type, y = AvgImdbScore, fill = Stream)) +
  geom_bar(stat = "identity", position=position_dodge()) + 
    scale_fill_manual(values=c('#999999','#E69F00')) + 
      labs(title = "Amazon vs Netflix IMDb Score")

ggplot(movies_series_avg_rating, aes(x = Type, y = AvgRottenTomatoesScore, fill = Stream)) +
  geom_bar(stat = "identity", position=position_dodge()) + 
    labs(title = "Amazon vs Netflix Rotten Tomatoes Score")
```

2. Find all rating categories average IMDb rating for both Netflix and Amazon
```{r}
amazon_rating_categories <- amazon %>% 
                              group_by(rating) %>% 
                              summarize(AvgImdbScore = mean(na.omit(IMDb)), 
                                        AvgRottenTomatoesScore = mean(na.omit(`Rotten Tomatoes`))) %>% 
                              filter(!rating %in% c("NOT_RATE", "UNRATED", NA))

netflix_rating_categories <- netflix %>% 
                              group_by(`View Rating`) %>% 
                              summarize(AvgImdbScore = mean(na.omit(`IMDb Score`)), 
                                        AvgRottenTomatoesScore = mean(na.omit(`Rotten Tomatoes Score`))) %>% 
                              filter(!`View Rating` %in% c("Not Rated", "Unrated", NA))

ggplot(amazon_rating_categories, aes(x = rating, y = AvgImdbScore, fill = rating)) +
  geom_bar(stat = "identity", position=position_dodge()) + 
      labs(title = "Amazon Rating Categories Average IMDb Score") + 
        theme(text = element_text(size=10), axis.text.x = element_text(angle = 90, hjust=1))

ggplot(netflix_rating_categories, aes(x = `View Rating`, y = AvgImdbScore, fill = `View Rating`)) +
  geom_bar(stat = "identity", position=position_dodge()) + 
      labs(title = "Netflix Rating Categories Average IMDb Score") + 
        theme(text = element_text(size=10), axis.text.x = element_text(angle = 90, hjust=1))
```

3. From both Amazon and Netflix data set, list top 10 director(s) based on the average IMDb score.
```{r, message=FALSE, warning=FALSE}
newAmazon <- amazon %>% 
              mutate(director = strsplit(director, ",")) %>% 
              unnest(director) %>% 
              group_by(Title) %>% 
              mutate(`Director Name` = row_number()) %>% 
              spread(`Director Name`, director, sep = "")

newNetflix <- netflix %>% mutate(Director = strsplit(Director, ",")) %>% 
              unnest(Director) %>% 
              group_by(Title) %>% 
              mutate(`Director Name` = row_number()) %>% 
              spread(`Director Name`, Director, sep = "")

newAmazon <- newAmazon %>% select(Title, 
                                  IMDb, 
                                  `Director Name1`, 
                                  `Director Name2`, 
                                  `Director Name3`, 
                                  `Director Name4`, 
                                  `Director Name5`, 
                                  `Director Name6`, 
                                  `Director Name7`, 
                                  `Director Name8`, 
                                  `Director Name9`, 
                                  `Director Name10`)

newNetflix <- newNetflix %>% select(Title, 
                                    `IMDb Score`, 
                                    `Director Name1`, 
                                    `Director Name2`, 
                                    `Director Name3`, 
                                    `Director Name4`, 
                                    `Director Name5`, 
                                    `Director Name6`, 
                                    `Director Name7`, 
                                    `Director Name8`, 
                                    `Director Name9`, 
                                    `Director Name10`, 
                                    `Director Name11`)

grouped_newAmazon <- newAmazon %>% 
                      group_by(`Director Name1`, 
                               `Director Name2`, 
                               `Director Name3`, 
                               `Director Name4`, 
                               `Director Name5`, 
                               `Director Name6`, 
                               `Director Name7`, 
                               `Director Name8`, 
                               `Director Name9`, 
                               `Director Name10`) %>% 
                      summarize(AvgIMDbScore = mean(IMDb, na.rm = TRUE)) %>% 
                      unite("Director", `Director Name1`:`Director Name10`, na.rm = TRUE, remove = TRUE, sep = ",") %>% 
                      arrange(desc(AvgIMDbScore)) %>% head(10)

grouped_newNetflix <- newNetflix %>% 
                        group_by(`Director Name1`, 
                                 `Director Name2`, 
                                 `Director Name3`, 
                                 `Director Name4`, 
                                 `Director Name5`, 
                                 `Director Name6`, 
                                 `Director Name7`, 
                                 `Director Name8`, 
                                 `Director Name9`, 
                                 `Director Name10`, 
                                 `Director Name11`) %>% 
                        summarize(AvgIMDbScore = mean(`IMDb Score`, na.rm = TRUE)) %>% 
                        unite("Director", `Director Name1`:`Director Name11`, na.rm = TRUE, remove = TRUE, sep = ",") %>% 
                        arrange(desc(AvgIMDbScore)) %>% head(10)

ggplot(grouped_newAmazon, aes(x = Director, y = AvgIMDbScore, fill = Director)) +
  geom_bar(stat = "identity", position=position_dodge()) + 
      labs(title = "Top 10 Directors in Amazon Prime dataset based on average IMDb score") + 
        theme(text = element_text(size=10), axis.text.x = element_text(angle = 90, hjust=1))

ggplot(grouped_newNetflix, aes(x = Director, y = AvgIMDbScore, fill = Director)) +
  geom_bar(stat = "identity", position=position_dodge()) + 
      labs(title = "Top 10 Directors in Netflix dataset based on average IMDb score") + 
        theme(text = element_text(size=8), axis.text.x = element_text(angle = 45, hjust=1))
```

4. For Netflix movies and TV shows, does receiving more awards imply high scores on IMDb?
```{r}
netflix_awards_received <- netflix %>% 
                            arrange(desc(`Awards Received`)) %>% 
                            distinct(Title, .keep_all = TRUE) %>% 
                            select(Title, `IMDb Score`, `Awards Received`) %>% 
                            head(10)

print(netflix_awards_received)
```

5. Determine top 5 movies and TV Show based on IMDb and Rotten Tomatoes for Netflix data set that is available in Malaysia.
```{r}
netflix_in_Malaysia <- netflix %>%
                        select(Title, `Country Availability`, `IMDb Score`, `Rotten Tomatoes Score`) %>%
                        mutate(`Country Availability` = strsplit(`Country Availability`, ",")) %>%
                        unnest(`Country Availability`) %>%
                        group_by(Title) %>%
                        mutate(`Country Show` = row_number()) %>%
                        spread(`Country Show`, `Country Availability`, sep = "") %>% 
                        pivot_longer(`Country Show1`:`Country Show36`, 
                                     names_to = "IMDB", 
                                     values_to = "Country") %>% 
                        select(Title, `IMDb Score`, `Rotten Tomatoes Score`, Country) %>% 
                        filter(!is.na(`Rotten Tomatoes Score`)) %>% 
                        filter(!is.na(`IMDb Score`)) %>% 
                        filter(!is.na(Country)) %>% 
                        filter(Country == "Malaysia")

imdb_netflix_in_Malaysia <- netflix_in_Malaysia %>% 
                            select(Title, `IMDb Score`, Country) %>% 
                            arrange(desc(`IMDb Score`)) %>% 
                            head(10)

rotten_netflix_in_Malaysia <- netflix_in_Malaysia %>% 
                              select(Title, `Rotten Tomatoes Score`, Country) %>% 
                              arrange(desc(`Rotten Tomatoes Score`)) %>% 
                              head(10)

rotten_netflix_in_Malaysia[rotten_netflix_in_Malaysia == "Attacking the Devil: Harold Evans and the Last Nazi War Crime"] <- "Attacking the Devil"

ggplot(imdb_netflix_in_Malaysia, aes(x = Title, y = `IMDb Score`, fill = Title)) +
  geom_bar(stat = "identity", position=position_dodge()) + 
      labs(title = "Top 10 Movie/TV Show on Netflix Malaysia from IMDb Score") + 
        theme(text = element_text(size=10), axis.text.x = element_text(angle = 90, hjust=1))

ggplot(rotten_netflix_in_Malaysia, aes(x = Title, y = `Rotten Tomatoes Score`, fill = Title)) +
  geom_bar(stat = "identity", position=position_dodge()) + 
      labs(title = "Top 10 Movie/TV Show on Netflix Malaysia from Rotten Tomatoes Score") + 
        theme(text = element_text(size=10), axis.text.x = element_text(angle = 90, hjust=1))
```
\
6. From Netflix data set, determine the top 5 countries with most movie/TV show available
```{r}
netflix_by_countries <- netflix %>%
                          select(Title, `Country Availability`, `IMDb Score`, `Rotten Tomatoes Score`) %>%
                          mutate(`Country Availability` = strsplit(`Country Availability`, ",")) %>%
                          unnest(`Country Availability`) %>%
                          group_by(Title) %>%
                          mutate(`Country Show` = row_number()) %>%
                          spread(`Country Show`, `Country Availability`, sep = "") %>% 
                          pivot_longer(`Country Show1`:`Country Show36`, 
                                       names_to = "IMDB", 
                                       values_to = "Country") %>% 
                          select(Title, `IMDb Score`, `Rotten Tomatoes Score`, Country) %>% 
                          filter(!is.na(Country))

grouped_by_countries <- netflix_by_countries %>% 
                        group_by(Country) %>% 
                        summarize(`Title Count` = n()) %>% 
                        arrange(desc(`Title Count`)) %>% 
                        head(10)

ggplot(grouped_by_countries, aes(x = Country, y = `Title Count`, fill = Country)) +
  geom_bar(stat = "identity", position=position_dodge()) + 
      labs(title = "Countries with most movies/TV Show") + 
        theme(text = element_text(size=10), axis.text.x = element_text(angle = 90, hjust=1))
```

7. From Amazon Prime data set, determine the top 5 Movie genre based on both average IMDb and Rotten Tomatoes score
```{r}

```